VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
added superscript comment

Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. The formal definition of the Cavalieri integral is given in Definition~\ref{def:cav_integral}.
It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader should only refer back to the definitions 
presented in this sections when things in Section~\ref{??} become unclear. Moreover, the definitions presented below were taken from [?]. Furthermore, none of the theorems in this sections are proved, the proofs are contained in [].

@@

>>>>

Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. The formal definition of the Cavalieri integral is given in Definition~\ref{def:cav_integral}.
It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader should only refer back to the definitions 
presented in this sections when things in Section~\ref{??} become unclear. Moreover, the definitions presented below were taken from [?]. Furthermore, none of the theorems in this section are proved, the proofs can be found in [].

@@

Note that the superscripts of the $x$-coordinates in the above definitions indicate to which partition, either $\mathcal{P}_1$ or $\mathcal{P}_2$, the $x$-coordinate in question belongs.
